% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Ryan C. Fleck}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{18 Eastwood Place, Apt 10}
  \moveleft.5\hoffset\centerline{Ottawa, ON  K1L 6X1}
 \moveleft.5\hoffset\centerline{ryan.fleck@protonmail.com}
 \moveleft.5\hoffset\centerline{1 613 501 4043}


\begin{resume}
 
\section{OBJECTIVE}  An internship or part-time position in the field of Computer or Software Engineering with special interest in GNU/Linux, data structures, information processing and Unix programming philosophies. Insatiable appetite for learning about new technology, niche languages, human behavior analytics and things to automate on my server.
 

\section{EDUCATION} {\sl Bachelor of Applied Science,} Engineering \\
                University of Ottawa, Ontario, graduating April 2020 \\
                Specialization: Computer Engineering
                
                {\sl Gifted High School Diploma with Honors} \\
                Westmount Charter School, Calgary, AB, graduated June 2015
 
 
\section{COMPUTER \\ SKILLS} {\sl Programming and Formatting Languages:} Java, C, Python 2.7/3, 
                cLISP, Haskell, Shell Scripting, MATLAB, C++(Arduino), HTML/CSS, LaTeX, Markdown.\\
                {\sl Operating Systems:} GNU/Linux, FreeBSD, MS Windows. \\
                 {\sl GNU/Linux Distributions:} Debian and derivatives like Ubuntu, RedHat Enterprise and derivatives like Fedora, SUSE Enterprise and derivatives like Tumbleweed, Arch.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Very comfortable in command line environments, especially bash
                \item Experienced with most of the core GNU applications and utilities
                \item Heavy user of ssh and associated light security/encryption protocols
                \item VCS enthusiast, uses Git with personal files, school and projects
                \item Proficiency with Microsoft Office Suite and alternatives.
\end{itemize}

\section{NOTABLE \\ QUALITIES} 
{\sl Customer Service Experience} - Has worked in restaurants, coffee shops and retail.\\
{\sl Can Write} - Keeps a journal, writes short stories and poetry, appreciates verbosity.\\
{\sl Communication Skills} - Able to convey ideas with clarity, good at teaching others.\\
{\sl Honest} - Will always be open about mistakes made, appreciates critical feedback.\\
{\sl Clever} - Finds the alternative. Who needs a powerful laptop when there's \$ssh -XC?\\
{\sl Helpful} - Will go out of his way to help peers with complex or poorly defined material.

\section{EXPERIENCE} {\sl Partner at Starbucks Coffee} \hfill Summer 2017 - Ongoing \\
                Barrister, Cashier, Support - Rideau Ctr, Ottawa, ON.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Valued member of the team with excellent customer service skills.
                \item  Ensures efficient operation of the store, rarely mismarks cups
                \end{itemize}
 
 {\sl General Laborer at Advantage Personnel} \hfill    Summer 2017 \\
                Contract light industrial, warehouse, dispatch, construction work - Ottawa, ON.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Courier Assistant for MIDLAND - Delivered pallets, night shift
                 \item Warehousing worker for various contractors. Heavy lifting
                 \item Demolished and restored many buildings in downtown and rural Ottawa, including a Swiss Chalet, Sushi joint, French School and many private residences
\item Construction work- Digging, basic carpentry, can operate many basic machines
                 \end{itemize} 
 
 
 
                {\sl Personal Shopper at Loblaws} \hfill            Summer 2016 - Winter 2017 \\
                Click and Collect Department - MacArthur Ave, Vanier, ON.
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Prepared groceries for pickup by customers
                 \item Interacted directly with customers to confirm details and problems with order
                 \item Never missed a shift, was never late to work
                 \end{itemize} 
                 
                {\sl Waiter at Jubilations} \hfill        Summer 2015 \\
               	Waited tables and completed tasks backstage - Dinner Theater - Calgary, AB.
\begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Had to remain in character related the the current show
                 \item Managed food and drinks for a section of up to 8 tables with 2-8 people each
                 \end{itemize} 
                   
                {\sl Staff at PAWS} \hfill        Summer 2015 \\
Inventory Management, Customer Service - Calgary, AB      
\begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Tasked with pricing goods and submitting orders for more product
                 \item Helped customers make informed decisions based on their unique requirements
                 \end{itemize}          	

 \section{COMMUNITY \\ SERVICE}  Organized and directed tutoring sessions for Introduction to Programming I (ITI1120). Helped to troubleshoot assignments and walked through generic solutions to common problems with a large group of students by bringing a personal projector to the library. One peer commented that my sessions were {\sl "Twice as useful as going to class."}\\
\\Tutored young children in Mathematics, English and Programming while attending classes at Westmount Charter School in Calgary, AB.


\section{EXTRA-CURRICULAR \\ ACTIVITIES}        
Administrator of a tiny Debian server for personal/friend use.\\     
           	Actor and Model for various agencies. Separate resume available.\\
           	Develops games using the LibGDX and GameMaker engines. \\
           	Refurbishes Thinkpads - Screen replacements, cleaning, rewiring.\\
           	Can paint, draw, sculpt and write both physically and digitally.\\
           	Participant in Pebble Smartwatch Hack-a-thon. Implemented a watchface in C.
           	
 
\section{SPECIFIC \\ LANGUAGE \\ EXPERIENCE}        
{\sl Java} - All school projects are completed in Java. Also used for many personal projects.\\
{\sl Python} - First programming language. Heavily utilized in personal sysadmin.\\
{\sl Shell Scripting} - Uses shell scripts to quickly get new systems up and running.\\
{\sl Haskell} -  Tinkered with while taking a statistics course, along with R and cLISP.\\
{\sl C} - Used to build a Pebble Watch-face and a number of small, simple programs.\\
{\sl MATLAB} - Used during 'Signals and Systems,' signal processing class ELG3125.\\
{\sl LaTeX} -  Used for assignments, labs and reports. Personal favorite for formatting.\\
{\sl Miscellaneous Scripting Languages} -  Give me a cheat sheet and a weekend.\\
{\sl In my Queue} - LISPs, Erlang, Rust, Hadoop, functional programming in general.
           	
\section{SOCIAL \\ MEDIA}        
{\sl Github} - github.com/ryanfleck \\
{\sl Linkedin} - linkedin.com/in/ryan-fleck-b5769412a \\
{\sl Facebook} - facebook.com/ryan.fleck.585 \\
{\sl Twitter} - No account. \\
{\sl Instagram} - instagram.com/rcflexx \\
{\sl Personal Website} - ryanfleck.github.io \\
 
 \vfill
 {\hfill\large\bf ryanfleck.github.io}
 

\end{resume}
\end{document}




