%-------------------------
% Ryan Fleck - Resume in Latex
% Template Author : Sourabh Bajaj
% Template License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\definecolor{rcf-gray}{gray}{0.90}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
  }{}{0em}{}[\color{rcf-gray}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://ryanfleck.github.io}{\Large Ryan Fleck}} & Email : \href{mailto:ryan.fleck@protonmail.com}{ryan.fleck@protonmail.com}\\
  \href{http://ryanfleck.github.io}{ryanfleck.github.io} & Mobile : +1 (613) 501-4043 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Ottawa}{Ottawa, ON}
      {Bachelor of Applied Science in Computer Engineering}{Sep. 2015 -- Apr. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {MNP LLP}{Kanata, ON}
      {Co-Op Developer}{Jan. 2018 - Dec. 2018}
      \resumeItemListStart
        
        \resumeItem{SiteCore -- C\#, Razor, JS, XML, MongoDB, SQL}
          {SiteCore is an Enterprise WCMS. Involved in quality assurance, testing, debugging, extending the backend and building components according to client requirements. }
       
        
      
       \resumeItem{Adobe Experience Manager -- JSP, Java, JS, HTL}
          {Assisted software architects with development of an AEM prototype for a client bid. Responsible for security, user \& group management, workflow and 2 components.}
    
       \resumeItem{TeamSite -- XML, XSL, Java, JS, Spring, Bootstrap, CentOS}
          {Maintained, debugged and extended an OpenText Teamsite system, a Java-based Spring Boot CMS. Utilized CI and CD in an agile team of five.}
          
          \resumeItem{Drupal -- PHP, Twig, JS, MariaDB, Azure}
          {Investigated, developed and deployed a Drupal CMS to Azure in a team of three. Responsible for CentOS container prototype, components, search page.}  
      
       \resumeItem{Technical Writing -- LaTeX, Python}
          {Produced high-quality documentation for both non-technical and system administrator targets. Minimal revision was applied to system documentation before submission to clients.}
      
       \resumeItem{Quality Assurance -- Microsoft TFS, Jira, Python}
          {Designed and executed multiple successful Quality Assurance Protocols, utilized automated testing, hundreds of bugs captured, tracked and resolved.}
      
      
      
      \resumeItemListEnd

    \resumeSubheading
      {Xalgorithms Foundation}{Ottawa, ON}
      {Contributing Developer \& Technical Writer}{Apr. 2018 - Present}
      \resumeItemListStart
        \resumeItem{Interpreter Development -- Scala, Ruby, Docker}
          {The IoR Interpreter parses rules in .xalgo format and runs them against an internal collection of tables and provided sample data. Coded some methods and unit tests.}
        \resumeItem{IoR Software Architecture}
          {Involved in discussions regarding the implementation of the IoR and .xalgo language. For more information, please visit \href{https://xalgorithms.org/}{xalgorithms.org}.}
        \resumeItem{Quality Assurance}
          {Investigates the , posts all bugs to the \href{https://github.com/Xalgorithms}{Xalgorithms Github repositories}.}

      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Personal Projects}
Projects are unit tested with \textbf{Travis CI}, often in a \textbf{Heroku} container, and available for code review on \href{https://github.com/ryanfleck}{Github}.
  \resumeSubHeadingListStart
    \resumeSubItem{Video Games -- Three.JS, Pixi.JS, LibGDX, Unreal, Socket.IO}
      {Numerous 1-4 player titles, usually written and tested for use with four XBox 360 controllers, using Express and Socket.IO for game networking.}
    \resumeSubItem{MorningData -- C++, NodeJS}
      {A seven-segment display sits by my bed and displays the weather, and the arrival time of the next bus at a fixed stop. System composed of an Arduino reading serial input and NodeJS piping formatted OC-Transpo and OpenWeatherMap API Data to a serial port. Next phase: wireless module to connect pi and arduino.}
    \resumeSubItem{SuperPull -- NodeJS}
      {Crawls the filesystem for git directories and stores them in a config file. Executing \emph{superpull} brings all configured repositories and remote branches up to date.}
    \resumeSubItem{RML: Ryan's Micro LISP -- C}
      {Tiny not-quite-ANSI lisp repl.  Tokenization and parsing experiment.}
    \resumeSubItem{NodeJS REST APIs -- PostgreSQL, Mongo, NodeJS, Express}
      {Built multiple NodeJS APIs, using clever async database storage \& retrieval methods, for projects and internship applications. Most recent: \href{https://github.com/RyanFleck/Shopify-Challenge-S19}{S19 Shopify Dev Challenge}}
  \resumeSubHeadingListEnd
  
%-----------PROJECTS-----------------
\section{Group Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{CanUX Conference Booth Trivia: NodeJS, Socket.IO, WebPack, Heroku, SASS}
      {Chat \& Trivia app that originated as a personal project, but was poached by MNP LLP and a frontend developer was assigned to design a frontend.}
    \resumeSubItem{BusBot: NodeJS, MongoDB}
      {Developed with M.Orchard. Developed a Slack Bot that pulls \& processes data from the OC-Transpo API and formats it for display in slack messages. Caches bus data in MongoDB.}
       \resumeSubItem{LightShow: Blockchain Christmas Tree -- NodeJS, Express, Solidity, C++}
      {Hackathon team of three. Utilized a simulated Ethereum blockchain to record transactions from a simple web app. Judges could use the app to change the color of the tree. Wrote the Node-to-Arduino serial interface for the dApp and the Arduino serial interpreter.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
