% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Ryan C. Fleck}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{ryan.fleck@protonmail.com $\cdot$ 1 (613) 501-4043 $\cdot$ ryanfleck.github.io}

\begin{resume} 

\section{EDUCATION} {\sl Bachelor of Applied Science} Computer Engineering \\
                University of Ottawa, Canada. Graduating April 2021
                
\section{EXPERIENCE} 
{\sl .NET Developer at MNP LLP} \hfill Dec 2018 - Jan 2018\\
Software Development position. Self-driven CO-OP. Some information under NDA.
\begin{itemize}  \itemsep -2pt %reduce space between items
\item {\sl Quality Assurance} - Developed and applied the QA protocol for a 5mo project.
\item {\sl Technical Writing} - Responsible for writing client-ready documentation.
\item {\sl Web Development} - Learned HTML/CSS/JS while assisting with frontend.
\end{itemize}
                
{\sl Xalgorithms Contributor} \hfill May 2018 - Present\\
Assisted with the development of the Xalgo language.
\begin{itemize}  \itemsep -2pt %reduce space between items
\item {\sl Guinea Pig} - Bugtested the Xalgorithm language prototypes.
\end{itemize}
                
\section{COMPUTER \\ SKILLS} {\sl Programming Languages} - Java, C, Python 2.7/3, Shell Scripting, MATLAB, C++(Arduino).\\
                 {\sl Formatting Languages} - HTML, CSS, LaTeX, Markdown.\\
                {\sl Operating Systems} - GNU/Linux, FreeBSD, MS Windows. \\
                 {\sl GNU/Linux Distributions} - RHEL, Debian and SUSE Linux products, and their respective downstream distributions, for desktop and small-server use.\\
                 {\sl Version Control} - Uses GIT for personal file organization and school projects.\\
                 {\sl Networking} - Personal user of ssh, ftp and associated security protocols.\\
                 {\sl Linux SysAdmin} - Runs a Debian server for personal/friend use. 
                 
\section{WORKPLACE \\ SKILLS} 
 {\sl Documentation} - Proficient with the Microsoft Office Suite, Libreoffice and Latex.\\
{\sl Customer Service Experience} - Has worked in restaurants, coffee shops and retail.\\
{\sl Teamwork} - Has worked in teams on various job sites, excellent delegation skills.\\
{\sl Quality of Writing} - Appreciates brevity, can communicate ideas effectively over email.\\
{\sl Honest} - Appreciates critical feedback and peer review, won't blame or hide mistakes.\\
{\sl Helpful} - Will go out of his way to help peers with complex or poorly defined material.



\section{PERSONAL \\ PROJECTS}     
{\sl Server} - Maintains a Debian server for Mumble, a personal cloud, remote computing.\\   
{\sl Blog} - Built a site using Ruby and the Jekyll static site generator. Project blog.\\   
{\sl BCOM} - Top-down turn-based strategy game implemented in Java based LibGDX.\\
{\sl GameMaker Engine} - Has made a handful of 1-4 player, 2-D physics games.\\
{\sl Art, Sound, Animation} - Creates assets for games using Krita, Gimp, Audacity, etc.\\
{\sl Hack-a-thon} - Participant in Pebble Smartwatch Hack-a-thon. Implemented in C.

\section{LANGUAGE \\ EXPERIENCE} 
{\sl C\#} - Implemented features and services while at MNP for a Sitecore CMS.\\
{\sl Java} - All school projects are completed in Java. Also used for many personal projects.\\
{\sl Python} - Personal tinkering language. Used at MNP to run unit tests with Selenium.\\
{\sl JavaScript} - Used during 'Signals and Systems,' signal processing class ELG3125.\\
{\sl C} - Used to build a Pebble Watch-face and a number of small, simple programs.\\
{\sl MATLAB} - Used during 'Signals and Systems,' signal processing class ELG3125.\\
{\sl LaTeX} -  Format assignments, labs and reports. Personal favorite for documentation..
{\sl In My Queue} - LISPs, C++, , 


\end{resume}
\end{document}




