\documentclass{article}
\begin{document}
\title{ELG2911-E Assignment 4}
\author{Ryan C Fleck \\ SN 8276723}

\maketitle

\section{Question 1}
\subsection{Part A}
The main difference between project and operational management is this:
\begin{itemize}
\item Project management can be defined as controlling a team, with the goal of planning and executing a project.
\item Operation management can be defined as designing and maintaining a process to produce services, intermediate goods or final goods.
\end{itemize}
The key difference here is the scope of the management: Project management has variable scalel and focuses on achieving a goal, like designing a product, whereas operations management is the longer-term design and production of goods and services. Both management types are responsible for ensuring that their goals are achieved in an efficient and effective manner. 
\subsection{Part B}
\begin{enumerate}
\item Company name: Go-Yoyo Toys.
\item Project goal: Design a yoyo.
\item Yoyo properties:
\begin{enumerate}
\item Tangle-free cord.
\item Is a yoyo.
\end{enumerate}
\item Project team members:
\begin{enumerate}
\item Development: Fred, Alex and John.
\item Financing: Frank
\end{enumerate}
\item Budget: \$46,000.00
\item Deadline: Christmas Show at NAC.
\end{enumerate}

\section{Question 2}
\subsection{Part A}
By reducing the time of D and F by one day each, the branches between the completion of {\it A.2} and initiation of {\it I.3} can be completed in 8 days instead of 9, with the longest time needed to follow a path being B,C,E at 8 days.
\subsection{Part B}
The project manager can shorten {\it A, B, C, E,} or {\it I} by one day, or remove {\it C} to complete the project one day early.
\section{Question 3}
AI Hair Salon tool risk register responses:\\(Avoid, transfer, mitigate, exploit, share or enhance.)
\begin{enumerate}
\item Negative risk. Mitigate effects by finding replacement.
\item Negative risk. Avoid effects by purchasing insurance.
\item Negative risk. Avoid effects by hiring more staff.
\item Positive risk. Exploit by advertising.
\end{enumerate}


\end{document}